Light inextensible strings under tension in the Schwarzschild geometry

### 2020-01-03 string_european_journal_of_physics.tex
use \Or for order O() as per the style guide
do not use amsmath as per the style guide
left align equations as per the style guide
log -> ln as per the style guide
order of brackets {[()]} as per the style guide
noindent after an equation
clarification of notation

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{units}
\usepackage{xcolor}
\modulolinenumbers[5]

@@

\end{frontmatter}
\newcommand{\rmd}{\mathrm{d}}

@@

% \begin{equation}\label{radial_string_length_properunits}
%   \int_{r=r_1}^{r_2}\frac{dr}{\sqrt{1-1/r}}=
%   \left.
%   \sqrt{r(r-1)} +\frac{1}{2}\log\left(
%   \frac{\sqrt{r}+\sqrt{r-1}}{\sqrt{r}-\sqrt{r-1}}\right)
%   \right|_{r_1}^{r_2}
%   \end{equation}

\begin{equation}\label{radial_string_length}
  \int_{r=r_1}^{r_2}\frac{\rmd r}{\sqrt{1-2M/r}}=
  \left.
  \sqrt{r(r-2M)} +\frac{1}{2}\log\left(
  \frac{\sqrt{r}+\sqrt{r-2M}}{\sqrt{r}-\sqrt{r-2M}}\right)
  \right|_{r_1}^{r_2}
  \end{equation}

@@

 \begin{equation}\label{ell}
   \ell =
   \int_{r=2M}^{r=2M(1+w)}\rmd s
   =2M\left(2\sqrt{w} + \frac{1}{3}w^{3/2} + O(w^{5/2})\right)
 \end{equation}

(compare the flat space string length of $2Mw$).  This would indicate
 that, close to the Schwarzschild radius $r=2M$, large (but finite)
 amounts of string are required to connect two points with slightly
 differing radial coordinates.  Passing to the case $w\gg 1$ we have
 an asymptotic expansion that begins

% \begin{equation}\label{asymptotic_ell_properunits}
%   \ell = w +  \frac{1}{2}\log w + \frac{1}{2} + \log(2)  +  \frac{1}{8}w^{-1} + O(w^{-2}),
% \end{equation}
% 
\begin{equation}\label{asymptotic_ell}
  \ell = 2M\left(w +  \frac{1}{2}\log w + \frac{1}{2} + \log(2)  +  \frac{1}{8}w^{-1} + O(w^{-2})\right),
\end{equation}

@@

\begin{figure}[p]
\centering
\includegraphics[width=\linewidth]{light_start_at_r_equals_2.pdf} % created by "angle_start_at_r_equals_2.R"
\caption{Null geodesics passing through $(4M,0)$ at different angles,
  shown for $0\leqslant\phi\leqslant 2\pi$}
\label{light_r_equals_2}
\end{figure}

>>>>

\documentclass[review,fleqn]{elsarticle}

\usepackage{lineno,hyperref}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{units}
\usepackage{xcolor}
\modulolinenumbers[5]

@@

\end{frontmatter}
\newcommand{\rmd}{\mathrm{d}}
\newcommand{\Or}{\mathord{\mathrm{O}}}

@@

% \begin{equation}\label{radial_string_length_properunits}
%   \int_{r=r_1}^{r_2}\frac{dr}{\sqrt{1-1/r}}=
%   \left.
%   \sqrt{r(r-1)} +\frac{1}{2}\ln\left(
%   \frac{\sqrt{r}+\sqrt{r-1}}{\sqrt{r}-\sqrt{r-1}}\right)
%   \right|_{r_1}^{r_2}
%   \end{equation}

\begin{equation}\label{radial_string_length}
  \int_{r=r_1}^{r_2}\frac{\rmd r}{\sqrt{1-2M/r}}=
  \left.
  \sqrt{r(r-2M)} +\frac{1}{2}\ln\left(
  \frac{\sqrt{r}+\sqrt{r-2M}}{\sqrt{r}-\sqrt{r-2M}}\right)
  \right|_{r_1}^{r_2}
  \end{equation}

@@

 \begin{equation}\label{ell}
   \ell =
   \int_{r=2M}^{r=2M(1+w)}\rmd s
   =2M\left[2\sqrt{w} + \frac{1}{3}w^{3/2} + \Or(w^{5/2})\right]
 \end{equation}

\noindent (compare the flat space string length of $2Mw$).  This would
indicate that, close to the Schwarzschild radius $r=2M$, large (but
finite) amounts of string are required to connect two points with
slightly differing radial coordinates.  Passing to the case $w\gg 1$
we have an asymptotic expansion that begins

% \begin{equation}\label{asymptotic_ell_properunits}
%   \ell = w +  \frac{1}{2}\ln w + \frac{1}{2} + \ln(2)  +  \frac{1}{8}w^{-1} + O(w^{-2}),
% \end{equation}
% 
\begin{equation}\label{asymptotic_ell}
  \ell = 2M\left[w +  \frac{1}{2}\ln w + \frac{1}{2} + \ln(2)  +  \frac{1}{8}w^{-1} + \Or(w^{-2})\right],
\end{equation}

@@

\begin{figure}[p]
\centering
\includegraphics[width=\linewidth]{light_start_at_r_equals_2.pdf} % created by "angle_start_at_r_equals_2.R"
\caption{Null geodesics passing through $(4M,0)$ at different angles,
  shown for $0\leqslant\phi\leqslant 2\pi$.  Notation as for figure~\ref{light_closest_approach}}
\label{light_r_equals_2}
\end{figure}
